\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-02-21 analysis/manuscript.Rmd
continuing discussions

As a consequence, libraries and their consortia began to develop licensing strategies aimed at avoiding such ‘double dipping’ scenarios, in which well-established commercial publishers gain twice from reading and open access publishing, as well as to increase publisher-provided immediate open access [@BJ_RK_2014; @Schimmer_2015].
These considerations resulted into transformative agreements, which cover a broad range of contracts between library consortia and publishers from mid-2010s onwards where institutional spending for subscriptions and open access publishing are considered together [@Borrego_2020; @Hinchliffe_2019].
Transformative agreements seek to control costs while allowing a transitional phase for publishing more open access articles. 
Similar to big deals, transformative agreements mainly bundle hybrid and subscription-only journals from commercial publishers, but aim at a higher degree of transparency than previous big deals, where contracts including payments were confidential [@Bergstrom_2014].
<!-- For example, the nationwide DEAL consortium in Germany, which includes universities and academic institutions, collectively cancelled their subscriptions with Elsevier from 2017 onwards to negotiate a transformative agreement [@Fraser_2023]. -->

@@

The controversies surrounding hybrid open access and transformative agreements have led to varying policy conclusions. 
For instance, the Association of Swedish Higher Education Institutions (Sveriges universitets- och
högskoleförbund, SUHF) recommended to only support agreements for publishing in full open access journals [^sweden].
Likewise, most cOAlition S funders will discontinue financial support for transformative agreements by the end of 2024 [@Liverpool_2023].
The consortium also removed most hybrid journals from its Transformative Journal program in 2023 due to publishers' failure to meet self-defined open access growth targets [@Brainard_2023]. 
In contrast, the German DEAL consortium signed a five-year transformative agreement with Elsevier starting in 2024, while also renewing its contracts with Springer Nature and Wiley until the end of 2028.

@@

The primary aim of this study was to investigate the adoption of open access in hybrid journals through transformative agreements, presenting a novel approach based on open data. 
The results indicate a steady increase, estimating that the majority of open access in hybrid journals in 2022 originate from institutions that had an transformative agreement in place. 
Yet, the majority of research literature published in hybrid journals between 2018 and 2022 remained behind a publisher paywall. 
Growth in the adoption of open access in hybrid journals through transformative agreements can be largely attributed to big three commercial publishers -- Elsevier, Springer Nature, and Wiley -- but varies across journals, publishers, subjects, and country affiliations. 
Despite limitations regarding the data used, the findings indicate that the current level of implementation of transformative agreements is insufficient to bring about a large-scale transformation to full open access.

Presenting an initial overview, some journals recorded substantial open access uptake rates through transformative agreements. Previous research indicate that these journals highlight specific areas where publisher portfolios already had strong market positions [@].

# Conclusions

@@

>>>>

As a consequence, libraries and their consortia began to develop licensing strategies aimed at avoiding such ‘double dipping’ scenarios, in which well-established commercial publishers gain twice from reading and open access publishing, as well as to increase publisher-provided immediate open access [@BJ_RK_2014; @Schimmer_2015].
These considerations resulted into transformative agreements[^agreements], which cover a broad range of contracts between library consortia and publishers from mid-2010s onwards where institutional spending for subscriptions and open access publishing are considered together [@Borrego_2020; @Hinchliffe_2019].
Transformative agreements seek to control costs while allowing a transitional phase for publishing more open access articles. 
Similar to big deals, transformative agreements mainly bundle hybrid and subscription-only journals from commercial publishers, but aim at a higher degree of transparency than previous big deals, where contracts including payments were confidential [@Bergstrom_2014].
<!-- For example, the nationwide DEAL consortium in Germany, which includes universities and academic institutions, collectively cancelled their subscriptions with Elsevier from 2017 onwards to negotiate a transformative agreement [@Fraser_2023]. -->

@@

The controversies surrounding hybrid open access and transformative agreements have led to varying policy conclusions. 
For instance, the Association of Swedish Higher Education Institutions (Sveriges universitets- och
högskoleförbund, SUHF) recommended to only support agreements for publishing in full open access journals [^sweden].
Likewise, most cOAlition S funders will discontinue financial support for transformative agreements by the end of 2024 [@Liverpool_2023].
The consortium also removed most hybrid journals from its Transformative Journal program in 2023 due to publishers' failure to meet self-defined open access growth targets [@Brainard_2023]. 
In contrast, the German DEAL consortium signed a five-year transformative agreement with Elsevier starting in 2024, while also renewing its contracts with Springer Nature and Wiley until the end of 2028. At the same time, the Colombia Consortium signed the first transformative agreements in Latin America [@Mu_oz_V_lez_2024].

@@

The primary aim of this study was to investigate the adoption of open access in hybrid journals in transformative agreements, which were introduced as a temporal means to support the transition of subscription-based academic publishing to full open access.
This study presents a novel approach based on open data, which leverages metadata on over 700 agreements and nine million journal articles to estimate the extent to which transformation agreement contribute to the transition of this journal business model based on institutional affiliation.
The results highlight a strong growth in open access between 2018 and 2022, particularly driven by an increasing number of institutions that had transformative agreements in place. 
Yet, the majority of research literature published in hybrid journals in this five-year period remained behind a publisher's paywall. 
Growth in the adoption of open access in hybrid journals, in particular through transformative agreements, can be largely attributed to three large commercial publishers -- Elsevier, Springer Nature, and Wiley -- but varies substantially across journals, publishers, subjects, and country affiliations. 
Despite the limitations of the data used, the findings indicate that the current level of implementation of transformative agreements is insufficient to bring about a large-scale transition to fully open access.

A key finding of the analysis is that transformative agreements increase market concentration. 
Specifically, the three largest commercial publishers—Elsevier, Springer Nature, and Wiley—have increased their market share in the context of open access, particularly in regard to open access provided through transformative agreements.
Together, the three publishers accounted for three-fourths of open access articles through transformative agreements, despite publishing less than half of the total publication volume published between 2018 and 2022.
This observation aligns with previous research on shifts in the publishing market following the introduction of funding opportunities for hybrid open access [@Jahn_2016; @Butler_2023; @Shu_2023]. 
Additionally, the results confirm previously observed variations by publisher, with Elsevier exhibiting a different development than Springer Nature and Wiley  [@Butler_2023; @Jahn_2021]. 
However, it must be noted that the focus of transformative agreements on publishers with large hybrid journal portfolios is intentional [@ifla].
Because of transformative agreements with a few large publishers, national consortia were able to substantially increased their country’s annual open access article volume [@Pinhasi_2021; @Huang_2020; @Taubert_2023; @Wenaas_2022].

Moreover, this study presents varying levels of open access uptake through transformative agreements across journals, which can be attributed to the alignment of authors' affiliations and the availability of such agreements at their institutions.
In line with previous research findings [@Butler_2023; @Jahn_2021], high uptake rates were observed across hybrid journals in the Social Sciences and Humanities.
However, it is important to emphasise that these hybrid journals do not encompass the entire field.
For example, a study by @Khanna_2022 found that approximately 60% of journals utilizing the open-source publishing platform Open Journal Systems (OJS) fall within the Social Sciences and Humanities. 
In these fields, the majority of full open access journals are so-called "Diamond OA journals" that do not charge publication fees [@bosman_2021_4558704].
Rather, this result can be more accurately attributed to the substantial proportion of authors from high-income countries who publish in these hybrid journals included in transformative agreements, particularly when journals are of local relevance, such as through the belonging to national societies or regional research scope.

 <!--   [funding options in the humanities and social sicences] -->
Surprisingly, the total publication output of high-income countries belonging to the OECD declined susbtantially between 2018 and 2022, while the BRICS countries recorded an steady increase. 
Because the BRICS expansion can be exclusivley attributed to closed access articles, this developement has the potential to hinder the transition of academic journal publishing to full open access through transformative agreements. 
In China, the most productive country according to the total article volume in hybrid journals, 
(shu und zhang und das indische paper)

other countries less represented and brazil diamond russia The Eastern Europe Expanded Collection

but not coherent acorss all countries, in particular in the us. neverthelles china and us have susbtantial market shares when it comes to hybrid oa.

There are at least three potential limitations
concerning the results of this study. A first limitation
concerns … A second potential limitation is that …

These data have some potential intervention implications. forst and formesot, the supprot recent pocliy decision highlighting a grew in oa at country-level, but questioning the. if thouse contracts, a transiliteration is ttoo short and might require a longer transiltierional period. the growtrh in brics however would require too impleis unboundling, other payment means and focus on alternative, in particular innovations like preprinting, diamond oa

In terms of future research, it would be useful to extend the current findings by examining other oa types, combine oa with mobility. fianncials tudies are also required to assess claims of cost-sensitive, here, publisher and publsiher are required to increase transparency. at the same time, studies needed to assess these claim economically. data can be improved to entail more, in apritcular consortia could start to disclose funded articles as , with openapc already a cwors-orucing platform available. also libraries can contrbute to an improved catalogiuing of transformative agreements including participating insitutions, which is aligned with standards used in schoalrly communications like ror id.

In summary, after more than tow decades, hybrid open access has not demonstrated a succesful menas. stduying transofrmative agreemnts, effects can be found at the -level of participating countries, but overlla uptake remains low, in particular with regard to publications from brocs countries, which country share rise, exclusively on the expense of closed access.  means

@@

[^agreements]: In this paper I use the term "transformative agreement", addressing also offsetting, read-and-publish or publish-and-read deals, and other variants [@Borrego_2020; @Hinchliffe_2019]. Although the term is critised as misleading and not useful to describe these agreements between library consortia and publishers [@budapest], it is widely used in policy discussions and in the research literature.

### 2024-02-21 analysis/manuscript.tex
continuing discussions

As a consequence, libraries and their consortia began to develop
licensing strategies aimed at avoiding such `double dipping' scenarios,
in which well-established commercial publishers gain twice from reading
and open access publishing, as well as to increase publisher-provided
immediate open access (Björk \& Solomon, 2014; Schimmer et al., 2015).
These considerations resulted into transformative agreements, which
cover a broad range of contracts between library consortia and
publishers from mid-2010s onwards where institutional spending for
subscriptions and open access publishing are considered together
(Borrego et al., 2020; Hinchliffe, 2019). Transformative agreements seek
to control costs while allowing a transitional phase for publishing more
open access articles. Similar to big deals, transformative agreements
mainly bundle hybrid and subscription-only journals from commercial
publishers, but aim at a higher degree of transparency than previous big
deals, where contracts including payments were confidential (Bergstrom
et al., 2014).

@@

By the end of 2023, many transformative agreements were implemented, but
interim outcomes are mixed. The ESAC Transformative Agreement
Registry\footnote{\url{https://esac-initiative.org/about/transformative-agreements/agreement-registry/}},
the largest source of disclosure, recorded more than 800 transformative
agreements, resulting in up to 900.000 open access articles published in
both full open access and hybrid journals according to the accompanying
ESAC Market Watch\footnote{\url{https://esac-initiative.org/market-watch/}}.
Library consortia reported increased open access volume, streamlined
payment and monitoring procedures, as well as extensive utilization of
open access options by the researchers they serve (Marques \& Stone,
2020; Parmhed \& Säll, 2023; Pinhasi et al., 2020). The ongoing
standardisation of transformative agreements contributed to improved
transparency in terms of contracts and publisher-provided article
metadata (Marques et al., 2019; Pinhasi et al., 2021). However, with the
growing trend toward transformative agreements, continued reliance on
big deals is perceived as problematic, because it perpetuate market
concentration (Butler et al., 2023; Shu \& Larivière, 2023). Whether
transformative agreements lead to reduced pricing remains uncertain
(Borrego, 2023) and a substantial transition of hybrid journals towards
full open access could not be observed (Matthias et al., 2019; Momeni et
al., 2021). The focus on large commercial publishers might also increase
inequality, because transformative agreements focus on pay to publish
open access mainly targets institutions from high-income countries,
furthering a questionable journal prestige culture (\textbf{budapest?}).
Besides, an editorial-board resignation raised concerns that publishers'
desire to maximize journal publication volume ``without regard to
quality'' is a consequence of transformative agreements (Rasmussen,
2023).

The controversies surrounding hybrid open access and transformative
agreements have led to varying policy conclusions. For instance, the
Association of Swedish Higher Education Institutions (Sveriges
universitets- och högskoleförbund, SUHF) recommended to only support
agreements for publishing in full open access journals \footnote{\url{https://www.su.se/english/news/open-access-need-to-move-away-from-transformative-agreements-1.683787}}.
Likewise, most cOAlition S funders will discontinue financial support
for transformative agreements by the end of 2024 (Liverpool, 2023). The
consortium also removed most hybrid journals from its Transformative
Journal program in 2023 due to publishers' failure to meet self-defined
open access growth targets (Brainard, 2023). In contrast, the German
DEAL consortium signed a five-year transformative agreement with
Elsevier starting in 2024, while also renewing its contracts with
Springer Nature and Wiley until the end of 2028.

@@

The primary aim of this study was to investigate the adoption of open
access in hybrid journals through transformative agreements, presenting
a novel approach based on open data. The results indicate a steady
increase, estimating that the majority of open access in hybrid journals
in 2022 originate from institutions that had an transformative agreement
in place. Yet, the majority of research literature published in hybrid
journals between 2018 and 2022 remained behind a publisher paywall.
Growth in the adoption of open access in hybrid journals through
transformative agreements can be largely attributed to big three
commercial publishers -- Elsevier, Springer Nature, and Wiley -- but
varies across journals, publishers, subjects, and country affiliations.
Despite limitations regarding the data used, the findings indicate that
the current level of implementation of transformative agreements is
insufficient to bring about a large-scale transformation to full open
access.

Presenting an initial overview, some journals recorded substantial open
access uptake rates through transformative agreements. Previous research
indicate that these journals highlight specific areas where publisher
portfolios already had strong market positions {[}@{]}.

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Bakker_2024}{}}%
Bakker, C., Langham-Putrow, A., \& Riegelman, A. (2024). Impact of
transformative agreements on publication patterns: An analysis based on
agreements from the ESAC registry. \emph{International Journal of
Librarianship}, \emph{8}(4), 67--96.
\url{https://doi.org/10.23974/ijol.2024.vol8.4.341}

@@

@@

@@

@@

>>>>

As a consequence, libraries and their consortia began to develop
licensing strategies aimed at avoiding such `double dipping' scenarios,
in which well-established commercial publishers gain twice from reading
and open access publishing, as well as to increase publisher-provided
immediate open access (Björk \& Solomon, 2014; Schimmer et al., 2015).
These considerations resulted into transformative agreements\footnote{In
  this paper I use the term ``transformative agreement'', addressing
  also offsetting, read-and-publish or publish-and-read deals, and other
  variants (Borrego et al., 2020; Hinchliffe, 2019). Although the term
  is critised as misleading and not useful to describe these agreements
  between library consortia and publishers (Babini et al., 2022), it is
  widely used in policy discussions and in the research literature.},
which cover a broad range of contracts between library consortia and
publishers from mid-2010s onwards where institutional spending for
subscriptions and open access publishing are considered together
(Borrego et al., 2020; Hinchliffe, 2019). Transformative agreements seek
to control costs while allowing a transitional phase for publishing more
open access articles. Similar to big deals, transformative agreements
mainly bundle hybrid and subscription-only journals from commercial
publishers, but aim at a higher degree of transparency than previous big
deals, where contracts including payments were confidential (Bergstrom
et al., 2014).

@@

By the end of 2023, many transformative agreements were implemented, but
interim outcomes are mixed. The ESAC Transformative Agreement
Registry\footnote{\url{https://esac-initiative.org/about/transformative-agreements/agreement-registry/}},
the largest source of disclosure, recorded more than 800 transformative
agreements, resulting in up to 900.000 open access articles published in
both full open access and hybrid journals according to the accompanying
ESAC Market Watch\footnote{\url{https://esac-initiative.org/market-watch/}}.
Library consortia reported increased open access volume, streamlined
payment and monitoring procedures, as well as extensive utilization of
open access options by the researchers they serve (Marques \& Stone,
2020; Parmhed \& Säll, 2023; Pinhasi et al., 2020). The ongoing
standardisation of transformative agreements contributed to improved
transparency in terms of contracts and publisher-provided article
metadata (Marques et al., 2019; Pinhasi et al., 2021). However, with the
growing trend toward transformative agreements, continued reliance on
big deals is perceived as problematic, because it perpetuate market
concentration (Butler et al., 2023; Shu \& Larivière, 2023). Whether
transformative agreements lead to reduced pricing remains uncertain
(Borrego, 2023) and a substantial transition of hybrid journals towards
full open access could not be observed (Matthias et al., 2019; Momeni et
al., 2021). The focus on large commercial publishers might also increase
inequality, because transformative agreements focus on pay to publish
open access mainly targets institutions from high-income countries,
furthering a questionable journal prestige culture (Babini et al.,
2022). Besides, an editorial-board resignation raised concerns that
publishers' desire to maximize journal publication volume ``without
regard to quality'' is a consequence of transformative agreements
(Rasmussen, 2023).

The controversies surrounding hybrid open access and transformative
agreements have led to varying policy conclusions. For instance, the
Association of Swedish Higher Education Institutions (Sveriges
universitets- och högskoleförbund, SUHF) recommended to only support
agreements for publishing in full open access journals \footnote{\url{https://www.su.se/english/news/open-access-need-to-move-away-from-transformative-agreements-1.683787}}.
Likewise, most cOAlition S funders will discontinue financial support
for transformative agreements by the end of 2024 (Liverpool, 2023). The
consortium also removed most hybrid journals from its Transformative
Journal program in 2023 due to publishers' failure to meet self-defined
open access growth targets (Brainard, 2023). In contrast, the German
DEAL consortium signed a five-year transformative agreement with
Elsevier starting in 2024, while also renewing its contracts with
Springer Nature and Wiley until the end of 2028. At the same time, the
Colombia Consortium signed the first transformative agreements in Latin
America (Muñoz-Vélez et al., 2024).

@@

The primary aim of this study was to investigate the adoption of open
access in hybrid journals in transformative agreements, which were
introduced as a temporal means to support the transition of
subscription-based academic publishing to full open access. This study
presents a novel approach based on open data, which leverages metadata
on over 700 agreements and nine million journal articles to estimate the
extent to which transformation agreement contribute to the transition of
this journal business model based on institutional affiliation. The
results highlight a strong growth in open access between 2018 and 2022,
particularly driven by an increasing number of institutions that had
transformative agreements in place. Yet, the majority of research
literature published in hybrid journals in this five-year period
remained behind a publisher's paywall. Growth in the adoption of open
access in hybrid journals, in particular through transformative
agreements, can be largely attributed to three large commercial
publishers -- Elsevier, Springer Nature, and Wiley -- but varies
substantially across journals, publishers, subjects, and country
affiliations. Despite the limitations of the data used, the findings
indicate that the current level of implementation of transformative
agreements is insufficient to bring about a large-scale transition to
fully open access.

A key finding of the analysis is that transformative agreements increase
market concentration. Specifically, the three largest commercial
publishers---Elsevier, Springer Nature, and Wiley---have increased their
market share in the context of open access, particularly in regard to
open access provided through transformative agreements. Together, the
three publishers accounted for three-fourths of open access articles
through transformative agreements, despite publishing less than half of
the total publication volume published between 2018 and 2022. This
observation aligns with previous research on shifts in the publishing
market following the introduction of funding opportunities for hybrid
open access (Butler et al., 2023; Jahn \& Tullney, 2016; Shu \&
Larivière, 2023). Additionally, the results confirm previously observed
variations by publisher, with Elsevier exhibiting a different
development than Springer Nature and Wiley (Butler et al., 2023; Jahn et
al., 2022). However, it must be noted that the focus of transformative
agreements on publishers with large hybrid journal portfolios is
intentional (Campbell et al., 2022). Because of transformative
agreements with a few large publishers, national consortia were able to
substantially increased their country's annual open access article
volume (Huang et al., 2020; Pinhasi et al., 2021; Taubert et al., 2023;
Wenaas, 2022).

Moreover, this study presents varying levels of open access uptake
through transformative agreements across journals, which can be
attributed to the alignment of authors' affiliations and the
availability of such agreements at their institutions. In line with
previous research findings (Butler et al., 2023; Jahn et al., 2022),
high uptake rates were observed across hybrid journals in the Social
Sciences and Humanities. However, it is important to emphasise that
these hybrid journals do not encompass the entire field. For example, a
study by Khanna et al. (2022) found that approximately 60\% of journals
utilizing the open-source publishing platform Open Journal Systems (OJS)
fall within the Social Sciences and Humanities. In these fields, the
majority of full open access journals are so-called ``Diamond OA
journals'' that do not charge publication fees (Bosman et al., 2021).
Rather, this result can be more accurately attributed to the substantial
proportion of authors from high-income countries who publish in these
hybrid journals included in transformative agreements, particularly when
journals are of local relevance, such as through the belonging to
national societies or regional research scope.

Surprisingly, the total publication output of high-income countries
belonging to the OECD declined susbtantially between 2018 and 2022,
while the BRICS countries recorded an steady increase. Because the BRICS
expansion can be exclusivley attributed to closed access articles, this
developement has the potential to hinder the transition of academic
journal publishing to full open access through transformative
agreements. In China, the most productive country according to the total
article volume in hybrid journals, (shu und zhang und das indische
paper)

other countries less represented and brazil diamond russia The Eastern
Europe Expanded Collection

but not coherent acorss all countries, in particular in the us.
neverthelles china and us have susbtantial market shares when it comes
to hybrid oa.

There are at least three potential limitations concerning the results of
this study. A first limitation concerns \ldots{} A second potential
limitation is that \ldots{}

These data have some potential intervention implications. forst and
formesot, the supprot recent pocliy decision highlighting a grew in oa
at country-level, but questioning the. if thouse contracts, a
transiliteration is ttoo short and might require a longer
transiltierional period. the growtrh in brics however would require too
impleis unboundling, other payment means and focus on alternative, in
particular innovations like preprinting, diamond oa

In terms of future research, it would be useful to extend the current
findings by examining other oa types, combine oa with mobility.
fianncials tudies are also required to assess claims of cost-sensitive,
here, publisher and publsiher are required to increase transparency. at
the same time, studies needed to assess these claim economically. data
can be improved to entail more, in apritcular consortia could start to
disclose funded articles as , with openapc already a cwors-orucing
platform available. also libraries can contrbute to an improved
catalogiuing of transformative agreements including participating
insitutions, which is aligned with standards used in schoalrly
communications like ror id.

In summary, after more than tow decades, hybrid open access has not
demonstrated a succesful menas. stduying transofrmative agreemnts,
effects can be found at the -level of participating countries, but
overlla uptake remains low, in particular with regard to publications
from brocs countries, which country share rise, exclusively on the
expense of closed access. means

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-budapest}{}}%
Babini, D., Chan, L., Hagemann, M., Joseph, H., Kuchma, I., \& Suber, P.
(2022). \emph{{The Budapest Open Access Initiative-20th. Anniversary
recommendations (BOAI20)}}.
\url{https://www.budapestopenaccessinitiative.org/boai20/}

\leavevmode\vadjust pre{\hypertarget{ref-Bakker_2024}{}}%
Bakker, C., Langham-Putrow, A., \& Riegelman, A. (2024). Impact of
transformative agreements on publication patterns: An analysis based on
agreements from the ESAC registry. \emph{International Journal of
Librarianship}, \emph{8}(4), 67--96.
\url{https://doi.org/10.23974/ijol.2024.vol8.4.341}

@@

\leavevmode\vadjust pre{\hypertarget{ref-bosman_2021_4558704}{}}%
Bosman, J., Frantsvåg, J. E., Kramer, B., Langlais, P.-C., \& Proudman,
V. (2021). \emph{OA diamond journals study. Part 1: findings}. Zenodo.
\url{https://doi.org/10.5281/zenodo.4558704}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ifla}{}}%
Campbell, C., Dér, Á., Geschuhn, K., \& Valente, A. (2022). How are
transformative agreements transforming libraries? In I. F. of Library
Associations \& I. (IFLA) (Eds.), \emph{87th IFLA world library and
information congress (WLIC) / 2022 in dublin, ireland}. IFLA.
\url{https://repository.ifla.org/handle/123456789/1973}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Khanna_2022}{}}%
Khanna, S., Ball, J., Alperin, J. P., \& Willinsky, J. (2022).
Recalibrating the scope of scholarly publishing: A modest step in a vast
decolonization process. \emph{Quantitative Science Studies},
\emph{3}(4), 912--930. \url{https://doi.org/10.1162/qss_a_00228}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Mu_oz_V_lez_2024}{}}%
Muñoz-Vélez, H., Pallares, C., Echavarría, A. F., Contreras, J., Pavas,
A., Bello, D., Rendón, C., Calderón-Rojas, J., \& Garzón, F. (2024).
Strategies for negotiating and signing transformative agreements in the
global south: The colombia consortium experience. \emph{Journal of
Library Administration}, \emph{64}(1), 80--98.
\url{https://doi.org/10.1080/01930826.2023.2287945}
